---
output:
  html_document:
    fig_caption: yes
    theme: spacelab
    toc: no
---
# **number of cross overs per chromosome 1- arabidopsis**

Load libraries and the data
```{r setup, include=FALSE}
# load the required libraries and functions
library(knitr)
library(markdown)
#opts_chunk$set(dev = 'pdf')
library(grid)
library(gridExtra)
library(ggplot2)
library(MASS)
library(reshape2)

## cusotom ggplot theme
source("~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/ggplot_theme.R")

```

...     

...  		

Arabidopsis recombination landscape data is published in the following manuscript   
[http://www.nature.com/hdy/journal/v108/n4/full/hdy201195a.html](http://www.nature.com/hdy/journal/v108/n4/full/hdy201195a.html).

...

Supplemental information from above manuscript is downloaded and is in the following folder [recombination_landscape](../recombination_landscape)

...

#### box plot of number of cross overs in progeny of different parental crosses of arabidopsis

```{r boxplot-pacbio, echo=FALSE, fig.width=12, fig.height=4}
table = read.delim(file="chromosome_1_crosses.txt")
table$X <- NULL
melted = melt(table)
ggplot(melted, aes(x=variable, y=value, fill=variable)) + geom_boxplot() +
labs(x ="crosses", y="num crossovers", main=NULL) + mytheme + theme(legend.position="none")

```


...


...


#### fitting distribtuion to number of cross overs per chromosome

```{r fit-distr, echo=FALSE, fig.width=12, fig.height=24}
library(fitdistrplus)

# small function to make density data frame from vector
den2df <- function(vector){
  den <- density(vector)
  df <- data.frame(x=den$x, y=den$y)
}

chr = 1 # chr number
size = 30427671 # bp
# empty data frame to store parameters for fitted gamma distribtuion
table1 <- data.frame(t(rep(NA,6)))
names(table1) <- c("chr", "size", "sample", "num_plants", "shape", "rate")
rows = 1
P <- list()
for (a in colnames(table) ) {
  vect = as.numeric(na.omit(table[,a]))
  inputdf = den2df(vect)
  len = length(vect)
  fitgam <- fitdist(vect, "gamma",method = "mme")
  gam = rgamma(len, shape=fitgam$estimate['shape'], rate=fitgam$estimate['rate'])
  gamdf = den2df(round(gam))
  table1[rows,] <- c(chr, size, a, len, fitgam$estimate['shape'], fitgam$estimate['rate'])
  
  #fitgeom <- fitdist(vect, "geom",method = "mme")
  #geom = rgeom(len, fitgeom$estimate)
  #geomdf = den2df(round(geom))
  #geom_line(data=geomdf,aes(x=x, y=y, colour="geometric"), size=1)

  fitpois <- fitdist(vect, "pois",method = "mme")
  pois = rpois(len, fitpois$estimate)
  poisdf = den2df(pois)
  
  fitnb <- fitdist(vect, "nbinom")
  nb = rnbinom(len, size=fitnb$estimate['size'], mu=fitnb$estimate['mu'])
  nbdf = den2df(nb)

  each_plot = ggplot() + geom_line(data=inputdf, aes(x=x, y=y, colour="raw data"), size=1) +
    geom_line(data=gamdf, aes(x=x, y=y, colour="gamma"), size=1) +
    geom_line(data=poisdf, aes(x=x, y=y, colour="poisson"), size=1) +
    geom_line(data=nbdf, aes(x=x, y=y, colour="nbinom"), size=1) +
    scale_y_sqrt() + mytheme + theme(legend.position=c(0.73,0.83)) +
    labs(x =NULL, y=NULL, main=NULL)
  P <- c(P, list(each_plot))
  rows = rows + 1
}

do.call(grid.arrange, c(P, nrow = 6, ncol= 3))

write.table(table1, file="chr1_gamma_params.txt", sep="\t", row.names = FALSE, quote=FALSE)
```



