---
output:
  html_document:
    fig_caption: yes
    theme: spacelab
    toc: no
---
# **cross overs positions individual chromosomes - arabidopsis**

Load libraries and the data
```{r setup, include=FALSE}
# load the required libraries and functions
library(knitr)
library(markdown)
#opts_chunk$set(dev = 'pdf')
library(grid)
library(gridExtra)
library(ggplot2)
library(MASS)
library(reshape2)
library(fitdistrplus)

## cusotom ggplot theme
source("~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/ggplot_theme.R")
source("~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/qqline2.R")
mytheme = mytheme + theme(legend.direction="horizontal", legend.position=c(0.5,0.9))

```

...     

...  		

Arabidopsis recombination landscape data is published in the following manuscript   
[http://www.nature.com/hdy/journal/v108/n4/full/hdy201195a.html](http://www.nature.com/hdy/journal/v108/n4/full/hdy201195a.html).

...

Supplemental information from above manuscript is downloaded and is in the following folder [recombination_landscape](../recombination_landscape)

...

...


#### plotting cross overs positions chromosome 1

```{r chr1, echo=FALSE, fig.width=12, fig.height=10}
table = na.omit(read.delim(file="chromosome_1_crossover_positions.txt"))
table = subset(table, Cross != "P17")

p1 = ggplot() + geom_line(data=table, aes(x=mid.point, y=XOs, colour = Cross)) +
  labs(x ="position in bp", y="num crossovers", main=NULL) + mytheme +
  guides(col = guide_legend(ncol = 8, byrow = TRUE))

pool_positions = function(df,id){
  table_out <- data.frame(t(rep(NA,3)))
  names(table_out) <- c("chr", "pos", "count")
  num = 1
  for (i in 1:nrow(df)) {
    if (is.element(df$mid.point[i], table_out$pos)){
      index = match(df$mid.point[i], table_out$pos)
      table_out$count = as.numeric(table_out$count)
      table_out$count[index] = table_out$count[index] + df$XOs[i]
    } else {
      table_out[num,] <- c(id, df$mid.point[i], df$XOs[i])
      num = num + 1
    }
  }
  table_out$pos = as.numeric(table_out$pos)
  table_out
}

new_table = pool_positions(table, "chr1")
new_table$prop = new_table$count/sum(new_table$count)
p2 = ggplot() + geom_line(data=new_table, aes(pos, prop)) +
  labs(x ="position in bp", y="proportion", main=NULL) + mytheme

gA <- ggplotGrob(p1)
gB <- ggplotGrob(p2)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

outtable = new_table

```


...


...

#### plotting cross overs positions chromosome 2

```{r chr2, echo=FALSE, fig.width=12, fig.height=10}
table = na.omit(read.delim(file="chromosome_2_crossover_positions.txt"))
table = subset(table, Cross != "P17")

p1 = ggplot() + geom_line(data=table, aes(x=mid.point, y=XOs, colour = Cross)) +
  labs(x ="position in bp", y="num crossovers", main=NULL) + mytheme +
  guides(col = guide_legend(ncol = 8, byrow = TRUE))

new_table = pool_positions(table, "chr2")
new_table$prop = new_table$count/sum(new_table$count)
p2 = ggplot() + geom_line(data=new_table, aes(pos, prop)) +
  labs(x ="position in bp", y="proportion", main=NULL) + mytheme

gA <- ggplotGrob(p1)
gB <- ggplotGrob(p2)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

outtable = rbind(outtable, new_table)
```


...


...

#### plotting cross overs positions chromosome 3

```{r chr3, echo=FALSE, fig.width=12, fig.height=10}
table = na.omit(read.delim(file="chromosome_3_crossover_positions.txt"))
table = subset(table, Cross != "P17")

p1 = ggplot() + geom_line(data=table, aes(x=mid.point, y=XOs, colour = Cross)) +
  labs(x ="position in bp", y="num crossovers", main=NULL) + mytheme +
  guides(col = guide_legend(ncol = 8, byrow = TRUE))

new_table = pool_positions(table, "chr3")
new_table$prop = new_table$count/sum(new_table$count)
p2 = ggplot() + geom_line(data=new_table, aes(pos, prop)) +
  labs(x ="position in bp", y="proportion", main=NULL) + mytheme

gA <- ggplotGrob(p1)
gB <- ggplotGrob(p2)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

outtable = rbind(outtable, new_table)
```


...


...

#### plotting cross overs positions chromosome 4

```{r chr4, echo=FALSE, fig.width=12, fig.height=10}
table = na.omit(read.delim(file="chromosome_4_crossover_positions.txt"))
table = subset(table, Cross != "P17")

p1 = ggplot() + geom_line(data=table, aes(x=mid.point, y=XOs, colour = Cross)) +
  labs(x ="position in bp", y="num crossovers", main=NULL) + mytheme +
  guides(col = guide_legend(ncol = 8, byrow = TRUE))

new_table = pool_positions(table, "chr4")
new_table$prop = new_table$count/sum(new_table$count)
p2 = ggplot() + geom_line(data=new_table, aes(pos, prop)) +
  labs(x ="position in bp", y="proportion", main=NULL) + mytheme

gA <- ggplotGrob(p1)
gB <- ggplotGrob(p2)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))


outtable = rbind(outtable, new_table)
```


...


...

#### plotting cross overs positions chromosome 5

```{r chr5, echo=FALSE, fig.width=12, fig.height=10}
table = na.omit(read.delim(file="chromosome_5_crossover_positions.txt"))
table = subset(table, Cross != "P17")

p1 = ggplot() + geom_line(data=table, aes(x=mid.point, y=XOs, colour = Cross)) +
  labs(x ="position in bp", y="num crossovers", main=NULL) + mytheme +
  guides(col = guide_legend(ncol = 8, byrow = TRUE))

new_table = pool_positions(table, "chr5")
new_table$prop = new_table$count/sum(new_table$count)
p2 = ggplot() + geom_line(data=new_table, aes(pos, prop)) +
  labs(x ="position in bp", y="proportion", main=NULL) + mytheme

gA <- ggplotGrob(p1)
gB <- ggplotGrob(p2)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

outtable = rbind(outtable, new_table)
write.table(outtable, file="pooled_xo_pos_at.txt", sep="\t", row.names = FALSE, quote=FALSE)
```


...


...

